Evolutionary Methods for Particle Swarm Movement

### 2014-05-07 docs/paper.tex
More tex stuff

Ever since Reynolds demonstrated that flocks of birds could be simulated as multi-agent systems, wherein each agent's motion is determined solely by local interactions, there has been interest in extending such systems to solve more general problems. Rodriguez, for example, added to each agent a goal-driven intelligence in the form of a finite state machine (FSM) that switched the agent between different sets of movement behaviors according to its local environment and current goal. He was able to demonstrate that a team of such agents was able to solve a resource locate-and-collect problem, and that a team programmed with flocking behaviors outperformed teams of agents that did not influence each other's movements.

@@

\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to {\LaTeX}}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

>>>>

Ever since Reynolds demonstrated that flocks of birds could be simulated as multi-agent systems, wherein each agent's motion is determined solely by local interactions, there has been interest in extending such systems to solve more general problems \cite{reynolds1987flocks}. Rodriguez, for example, added to each agent a goal-driven intelligence in the form of a finite state machine (FSM) that switched the agent between different sets of movement behaviors according to its local environment and current goal. He was able to demonstrate that a team of such agents was able to solve a resource locate-and-collect problem, and that a team programmed with flocking behaviors outperformed teams of agents that did not influence each other's movements.

@@

\bibliographystyle{plain}
\bibliography{paper}
